%!TEX program = xelatex
\documentclass[final]{report} %scrreprt of scrartcl
\input{../../.library/preamble.tex}
\input{../../.library/style.tex}
\addbibresource{../../.library/bibliography.bib}
\begin{document}
\chapter{Requirements}

\section{System Components}
\begin{itemize}
\item 2 train tracks
\item 2 crossing roads
\item 2 Barriers
\item 2 Pairs of flashing Lights
\item 2 Bells
\item 6 Train Sensors
\end{itemize}
\section{System Configuration}
TODO: insert schematic image
\section{Sequence}

\subsection{Barriers closing}
\begin{enumerate}
\item Lights start blinking
\item wait a few blinks, so noone is scared by an instant bell. %TODO[c]: is this what we want?
\item Bells start ringing
\item Wait for all the cars to drive off of the intersection and give them time to brake/react.
\item Barriers close
\end{enumerate}

\subsection{Barriers opening}
\begin{enumerate}
\item Barriers open
\item Bells stops ringing
\item Lights stop blinking
\end{enumerate}

\section{System Requirements}
The most obious requirement is of course that the system has to prevent cars from driving on the crossing when there is a train comming.

This means that the barriers have to be closed before a train enters the crossing and that they have to stay closed untill the crossing is clear of trains.

Besides this trivial requirement, there are a couple less trivial ones.
\begin{enumerate}
\item A train can arrive on both tracks from both directions.
	\begin{enumerate}
	\item When a train left the crossing and the barriers are opening again, a new train can retrigger the closing sequence again, which has priority over the opening sequence. %TODO: I wanted to write something there, but forgot what.
	\item Theoratically, it would be possible for two trains to arrive from the same direction where one of the trains is significantly shorter than the other one. %TODO: = Challenging Cases?
	\end{enumerate}

\item The beams, lights and bells on both sides of the track operate synchronously.
\end{enumerate}







\subsection{Challenging Cases}
	\begin{enumerate}
		\item Theoratically, it would be possible for two trains to arrive from the same direction where one of the trains is significantly shorter than the other one.

	\end{enumerate}

\section{Possible extensions}
\begin{enumerate}
\item Detect if Barriers are really closed (test feedback within the system)
\item Car detector to detect if all cars left the crossing
\item Add Signal Lights for trains to notify them the crossing is not clear
\item Adding an train sensor closer to the crossing so the system sooner knows that the tracks are clear.
\item 
\end{enumerate}



\begin{enumerate}
\item 
\end{enumerate}

\end{document}